Setting up Data

### 2020-02-03 src/SetupData.Rmd
removed juvi male mouse observations, re-ran MLH1

@@

```{r exclude.mice, echo=FALSE}
#remove mice -- 18nov17_WSB_f5 (only 1 cell)
exclude_mice_list <- c("10mar15_WSB_m2", "8oct14_WSB_f1", "8oct14_WSB_f3", "18nov17_WSB_f5",
                  "8jun15_G_f3", "8jun15_G_f4",
                  "4jan17_LEW_f2",
                  "8oct14_PWD_f3", "1apr15_PWD_f2", "8oct14_PWD_f5",
                  "12sep16_MSM_f3","31aug16_MSM_m2",
                  "27oct18_MOLF_m3",
                  "26oct18_SKIVE_f1","26oct18_SKIVE_f2","26oct18_SKIVE_f3",
                  "27aug18_CZECH_m1","8jun18_CZECH_m1",
                  "3sep18_AST_m1",
                  "3jel18_TOM_m1","3sep18_TOM_m1",
                  "31jul17_HMI_m1","3sep18_HMI_m1","3sep18_HMI_m2",
                 "21aug17_SPI_f1", "30may18_SPIC_f1", "30oct17_SPIC_m1", "8jun18_SPIC_m2"
                  )

MLH1_data <- MLH1_data[ ! MLH1_data$mouse %in% exclude_mice_list, ]
```

@@

#merge with DOB
mouse.table_w.Ages <- merge(batch.mouse.count.DF, meta.data, by.y = "mouse", by.x = "Var1", all = TRUE)
AP_mouse_table_w.Ages <- merge(AP_mouse_table.HQ, meta.data, by.y = "mouse", by.x = "mouse", all = TRUE)
#what are the differences between these two

#remove the NAs
AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[!(is.na(AP_mouse_table_w.Ages$category.x) | AP_mouse_table_w.Ages$category.x==""), ]
```

```{r Q1Q2.mouse.table, echo=FALSE}

#Make a mouse level table
Q12_mouse_table <- ddply(MLH1_data[MLH1_data$quality < 3,], c("mouse"), summarise,

@@

@@

male_mouse_table_w.good.ages <- male_mouse_table_w.Ages[male_mouse_table_w.Ages$age.weeks < 20,]
#droplevels on DF above

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_1.10.20.RData")

@@

-age (for males)
-enough cells
-both male and female

>>>>

to Do

- make sure to remove some of the juvi mice!! from the AP_mouse table

@@

```{r exclude.mice, echo=FALSE}
#remove mice -- 18nov17_WSB_f5 (only 1 cell)
exclude_mice_list <- c("10mar15_WSB_m2", "8oct14_WSB_f1", "8oct14_WSB_f3", "18nov17_WSB_f5",
                  "8jun15_G_f3", "8jun15_G_f4",
                  "4jan17_LEW_f2",
                  "8oct14_PWD_f3", "1apr15_PWD_f2", "8oct14_PWD_f5",
                  "12sep16_MSM_f3","31aug16_MSM_m2",
                  "27oct18_MOLF_m3",
                  "26oct18_SKIVE_f1","26oct18_SKIVE_f2","26oct18_SKIVE_f3",
                  "27aug18_CZECH_m1","8jun18_CZECH_m1",
                  "3sep18_AST_m1",
                  "3jel18_TOM_m1","3sep18_TOM_m1",
                  "31jul17_HMI_m1","3sep18_HMI_m1","3sep18_HMI_m2",
                 "21aug17_SPI_f1", "30may18_SPIC_f1", "30oct17_SPIC_m1", "8jun18_SPIC_m2"
                  )
MLH1_data <- MLH1_data[ ! MLH1_data$mouse %in% exclude_mice_list, ]

@@

#merge with DOB

#why are there 2
#mouse.table_w.Ages <- merge(batch.mouse.count.DF, meta.data, by.y = #"mouse", by.x = "Var1", all = TRUE)

AP_mouse_table_w.Ages <- merge(AP_mouse_table.HQ, meta.data, by.y = "mouse", by.x = "mouse", all = TRUE)
#what are the differences between these two

juvi.mice_DF <- AP_mouse_table_w.Ages[(AP_mouse_table_w.Ages$age.days < 15) & (AP_mouse_table_w.Ages$sex.y == "male"),]

juvi.mice_DF <- juvi.mice[!(is.na(juvi.mice$mouse) | juvi.mice$mouse==""), ]

#remove bad ages
AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[( (AP_mouse_table_w.Ages$age.weeks < 25) &  (AP_mouse_table_w.Ages$age.days != 13) ) | is.na(AP_mouse_table_w.Ages$age.weeks), ]

#remove juvi mice
MLH1_data <- MLH1_data[ ! MLH1_data$mouse %in% juvi.mice_DF$mouse, ]

#remove the NAs
AP_mouse_table_w.Ages <- AP_mouse_table_w.Ages[!(is.na(AP_mouse_table_w.Ages$category.x) | AP_mouse_table_w.Ages$category.x==""), ]

```{r Q1Q2.mouse.table, echo=FALSE}
#Make a mouse level table
Q12_mouse_table <- ddply(MLH1_data[MLH1_data$quality < 3,], c("mouse"), summarise,

@@

```{r Q123_mouse.table, echo=FALSE}

Q123_mouse_table <- ddply(MLH1_data[MLH1_data$quality < 4,], c("mouse"), summarise,

#REMOVE mice with fewer than 3 cells
Q123_mouse_table <- Q123_mouse_table[Q123_mouse_table$Ncells > 3,]

Q123_mouse_table <- add_strain(Q123_mouse_table)
Q123_mouse_table <- add_subsp(Q123_mouse_table)
Q123_mouse_table <- add_sex(Q123_mouse_table)
Q123_mouse_table <- add_category(Q123_mouse_table)

@@

#male_mouse_table_w.good.ages <- male_mouse_table_w.Ages[male_mouse_table_w.Ages$age.weeks < 20,]

male_mouse_table_w.good.ages <- male_mouse_table_w.Ages[( (male_mouse_table_w.Ages$age.weeks < 25) &  (male_mouse_table_w.Ages$age.days != 13) ) | is.na(male_mouse_table_w.Ages$age.weeks), ]

#remove juvi mice!!
#DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel[( (DF.HetC.MixedModel$age.weeks < 25) &  (DF.HetC.MixedModel$age.days != 13) ) | is.na(DF.HetC.MixedModel$age.weeks), ]

#droplevels on DF above

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_2.2.20.RData")

@@

- age (for males)
- enough cells
- both male and female
